---
title: "Hint for data visualisation with ggplot2 exercise"
author: "Tengku Muhammad Hanis"
date: '2023-09-19'
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, message = FALSE, warning = FALSE)
```

```{r warning=FALSE, message=FALSE}
library(tidyverse)
data("iris")
```

## Data

<details>
  <summary>Show explanation</summary>
We going to use iris data. See this [link](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/iris.html) for the description of the iris data.

```{r}
skimr::skim(iris)
```
</details>

## Question 1

Make histogram for variable Sepal.Length and give title for the histogram plot.

<details>
  <summary>Show hint</summary>
```{r cars}
ggplot(data = iris, mapping = aes(x = Sepal.Length)) +
  geom_histogram() +
  labs(title = "Histogram of Sepal.Length")
```
</details>

## Question 2

Make a scatter plot between variables Sepal.Width and Petal.Width and give different colors for each species (variable Species).

<details>
  <summary>Show hint</summary>
```{r}
ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Petal.Width, color = Species)) +
  geom_point() 
```
</details>

Next, separate the scatter plot, so that each species is its own plot.

<details>
  <summary>Show hint</summary>
```{r}
ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Petal.Width, color = Species)) +
  geom_point() +
  facet_grid(~Species)
```
</details>

## Question 3

Make a line plot on top of a scatter plot between variables Sepal.Length and Petal.Length and give different colors for each species (variable Species).

<details>
  <summary>Show hint</summary>
```{r}
ggplot(data = iris, mapping = aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  geom_line()
```
</details>
